\begin{abstract}
  Blockchains grow at a constant rate.
  When a client who holds only the genesis block first boots up, it
  needs to download data growing linearly in time---taking significant time to initialize---or
  rely on a trusted third party for its security.
  In the proof-of-work setting, numerous solutions of chain compression
  lift this burden from the clients and require only polylogarithmic data to be downloaded.
  However, the community has been advocating for the use of proof-of-stake,
  and most new systems abandon proof-of-work.
  Despite several attempts, compressing the proof-of-stake consensus state has achieved only a modicum
  of concrete improvement, but the asymptotic complexity remains linear.
  In this paper, we put forth a new construction that, for the first time, achieves sublinear
  communication complexity when bootstrapping a new proof-of-stake client. Our construction
  is in the standard model. Our scheme only makes use of hash functions and signature schemes
  and does not require a trusted setup. The proofs exchanged between the prover and the verifier
  on the network take the form of a Merkle tree of proof-of-stake epochs.
  Our key insight is to leverage
  the standard assumption that the verifier connects to at least one honest prover.
  The verifier enrolls the provers in a bisection game with a logarithmic
  number of interactions, in which the honest prover is destined to win once the adversarial
  Merkle tree is challenged at sufficient depth. As communication complexity is logarithmic
  in the execution time, our construction performs exponentially better than previous work.
  We prove our system is secure in the Ouroboros model,
  but our construction works in all modern systems such as Snow White and Algorand.
  In addition to superlight clients, our construction can be adopted to build efficient sidechains
  with proof-of-stake sources.
\end{abstract}
